---
title: "The effect of  macro variables on textbook downloads"
subtitle: "Analyzing 5 months of downloads from LibGen"
author: "Zolt&aacute;n Puha"
output:
  pdf_document:
    highlight: tango
    number_sections: yes
    toc: yes
    fig_caption: yes
    keep_tex: yes
    includes:
            in_header: header.tex
bibliography: reserch.bib
urlcolor: black
linkcolor: black
fontsize: 12pt
geometry: margin = 1.2in

abstract: "This thesis analyses download data obtained from one of the biggest online shadow library, LibGen. I only include textbooks in the analysed data. I research, whether price of the textbook or macro variables of different countries have effect on the number of downloads. I use regression analysis, using both OLS and hurdle regressions. I find that prices either have no or negative effect on downloads. A higher GDP, internet penetration or number of enrolled students into tertiary education all significantly increase the chance of downloads. " 
keywords: "illegal downloading, LibGen, data analysis, behavioral data"
---

\newpage

```{r child = 'litreview.Rmd'}
```

```{r child = 'models.Rmd'}
```



# Appendix

_Data analysis:_
I used Python 2.7 and MongoDB to build the dataset and tidy it, so it was ready for analysis. For analyzing and visualizing the data, I used R (version 3.3.1) and RStudio.

_Data discrapancy_

I checked for discrepancy in the data, by looking at the hour of downloads. The time in the dataset belongs to the server where the books are stored (Eastern-Europe), which makes it harder to derive the overall behavior per hour. However, the same trend can be seen through all of the countries. Here, I included three countries. Germany is the closest to the server from the three countries and it shows an expected behavior: the number of downloads are small during the night and increase during the daytime.

```{r, echo=FALSE, message=FALSE, fig.cap="Number of downloads per hour per country. Times in own timezone"}
print(hourplots)
```

_Regression with extensions_:

```{r, results='asis', echo=FALSE}
stargazer(mod_l1, mod_l2, header = FALSE, style = "qje", font.size = "tiny", float = TRUE, float.env = "table*")
```

_Regression with list price and DDC_:

```{r, results='asis', echo=FALSE}
stargazer(mod_ddc, header = FALSE, style = "qje", font.size = "tiny", float = TRUE, float.env = "table*", covariate.labels = c("List price", "DDC - 0",
                                                                                                                               "DDC - 1",
                                                                                                                               "DDC - 2",
                                                                                                                               "DDC - 3",
                                                                                                                               "DDC - 4",
                                                                                                                               "DDC - 5",
                                                                                                                               "DDC - 6",
                                                                                                                               "DDC - 7",
                                                                                                                               "DDC - 8",
                                                                                                                               "DDC - 9",
                                                                                                                               "List price*DDC - 1",
                                                                                                                               "List price*DDC - 2",
                                                                                                                               "List price*DDC - 3",
                                                                                                                               "List price*DDC - 4",
                                                                                                                               "List price*DDC - 5",
                                                                                                                               "List price*DDC - 6",
                                                                                                                               "List price*DDC - 7",
                                                                                                                               "List price*DDC - 8",
                                                                                                                               "List price*DDC - 9"))
```



_Regression for controlling for USA_: 
```{r, results='asis', echo=FALSE}
stargazer(reg_USAcontrol, header = FALSE, style = "qje", font.size = "small", float = TRUE, float.env = "table*", label = "usatable")
```

_Hurdle with regions_

```{r, results="asis", echo=FALSE, message=FALSE}
texreg(modelHurdle_region, float = TRUE, float.env = "table*", longtable = TRUE, dcolumn = TRUE, use.packages = FALSE, fontsize = "small", label ="hurdleregion")
```

_Hurdle with DDCs_

```{r, results="asis", echo=FALSE, message=FALSE}
texreg(modelHurdle_ddc, float = TRUE, float.env = "table*", longtable = TRUE, dcolumn = TRUE, use.packages = FALSE, fontsize = "small", label = "hurdleddc")
```



\newpage
\blandscape
```{r, results='asis', echo=FALSE}
stargazer(books_most_dt[,1:4, with = FALSE], summary = FALSE, header = FALSE,  title = "Top 3 downloaded books per DDC category", column.sep.width = "3pt",  font.size = "tiny", rownames = FALSE, label= "mostbyddc")
```
\elandscape

# References
